Pillar 2 - (STM) Topic Modeling

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
new documents

>>>>

#New Documents
##Align vocabulary
```{r}
mod.out #is model

#now we process the remaining documents
temp<-textProcessor(documents=gadarian$open.ended.response[101:nrow(gadarian)],
                    metadata=gadarian[101:nrow(gadarian),])

newdocs <- alignCorpus(new=temp, old.vocab=mod.out$vocab)
#we get some helpful feedback on what has been retained and lost in the print out.
#and now we can fit our new held-out documents

fitNewDocuments(model=mod.out, documents=newdocs$documents, newData=newdocs$meta,
                origData=out$meta, prevalence=~treatment + s(pid_rep),
                prevalencePrior="Covariate")

```
##Fit new docs
```{r}
#An example using the Gadarian data.  From Raw text to fitted model.
#(for a case where documents are all not processed at once see the help
# file for alignCorpus)
temp<-textProcessor(documents=gadarian$open.ended.response,metadata=gadarian)
out <- prepDocuments(temp$documents, temp$vocab, temp$meta)
set.seed(02138)
#Maximum EM its is set low to make this run fast, run models to convergence!
mod.out <- stm(out$documents, out$vocab, 3, prevalence=~treatment + s(pid_rep), 
              data=out$meta, max.em.its=5)
fitNewDocuments(model=mod.out, documents=out$documents[1:5], newData=out$meta[1:5,],
               origData=out$meta, prevalence=~treatment + s(pid_rep),
               prevalencePrior="Covariate")
